---
title: "Camping is In-tents"
author: "Irene Ryan, Pinn Janvatanavit, Truc Tran"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(macleish)
library(tidyverse)
library(sf)
library(leaflet)
library(RColorBrewer)
```

# Extracting Data[^1]

Here we simply extracted the macleish layers to make working with them easier.
```{r, message = FALSE}
trails <- macleish_layers[["trails"]]
boundary <- macleish_layers[["boundary"]]

streams <- macleish_layers[["streams"]]
wetlands <- macleish_layers[["wetlands"]]

forests <- macleish_layers[["forests"]]

research <- macleish_layers[["research"]]
buildings <- macleish_layers[["buildings"]]

landmarks <- macleish_layers[["landmarks"]]
challengecourses <- macleish_layers[["challenge_courses"]]

contours <- macleish_layers[["contours_3m"]]
```

# Points

In order to work with the coordinates listed in the instructions, we used a function that would convert them to latitude and longitude geometries. We also aggregated/tidied the forest layer so that all of the same forest types had their geometries together. The proj4-aea line was so we could convert the data to the Alber's Equal Area projection, which is in meters, so the data had an easy unit to work with.
```{r, message = FALSE}
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=42.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

point_to_sf <- function(lat, lon) {
  st_point(c(lat,lon)) %>%
    st_sfc(crs = 4326)
}

parking <- point_to_sf(-72.680663, 42.448013) %>%
  st_transform(crs = proj4_aea)

group_campsite <- point_to_sf(-72.678154, 42.450976) 

remote_campsite <- point_to_sf(-72.679581, 42.458549)

bechtel <- data.frame(lat = 42.449167, lon = -72.679389)

aggforests<-forests%>%
  group_by(Sheet1__Na)%>%
  summarise(n=n())
```

# Buffers

This was how we created the regions of plausible and impossible campsites. We converted them to the aea projection so we could work in meters, then converted them back to EPSG 4326 for mapping.
```{r, message = FALSE, warning = FALSE}
parking_buffer <- st_buffer(parking, dist = 804.672) %>%
  st_transform(crs = 4326)

streams_inside <- boundary %>%
  st_intersection(streams)

parkbuffer<-parking%>%
  st_transform(proj4_aea)%>%
  st_buffer(dist= 402.336)%>%
  st_transform(4326)
  
streams_buffer <- streams_inside %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 30.48) %>%
  st_transform(4326)

ccbuffer <- challengecourses %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)

researchbuffer  <-research %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)

wetlandbuffer <- wetlands %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)
```

# Palettes

These are the palettes for the forest types and the contours layer.
```{r, message = FALSE}
forestpalette <- colorFactor(palette = "viridis",
                    domain = aggforests$Sheet1__Na)

pale <- colorNumeric(palette = "inferno",
                    domain = contours$ELEV_M)
```

# Full exploration plot

Here we plotted ALL of the requirements at once. It's quite messy, but we ultimately pared it down using st_intersection/st_difference in the individual campsite plots.
```{r, message=FALSE}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = boundary, weight = 1, fillOpacity = 0.1) %>%
  addMarkers(data = st_transform(parking, crs = 4326), popup = "Parking") %>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite") %>%
  addPolygons(data = parking_buffer, color = "green") %>%
  addPolygons(data = buildings, weight = 1, opacity = 1) %>%
  addPolygons(data = parking_buffer, color = "green") %>%
  addPolylines(data = streams_buffer, fillOpacity = 0.5) %>%
  addPolygons(data = buildings, weight = 1, opacity = 1) %>%
  addPolygons(data = parking_buffer, color = "red") %>%
  addPolylines(data = streams_buffer, fillOpacity = 0.5, color="green") %>%
  addPolygons(data = researchbuffer,fillOpacity = 0, weight=.5)%>%
  addPolygons(data = ccbuffer, fillOpacity = 0, weight=.5)%>%
  addPolygons(data = wetlands)%>%
  addMarkers(data = challengecourses)%>%
  addPolygons(data = research)%>%
  addMarkers(lng = ~lon, lat = ~lat, data = bechtel,
             popup = "Bechtel Environmental Classroom") %>%
  addPolygons(data = contours, color = ~pale(ELEV_M), weight = 0.5) %>%
  addPolygons(data = wetlandbuffer, color = "green")%>%
  addLegend("bottomright", pal = pale, values = contours$ELEV_M, opacity = 1)

```

# Campsite 1

In order to find the regions we could place a site, we used a series of st_intersection() and st_difference on the buffers we created. You can see the highlighted areas in red where these intersections and differences coincide to give us the possible locations.
```{r, message = FALSE, warning = FALSE}
flatland <- contours %>%
  filter(ELEV_M<=220)

flatparking <- flatland %>%
  st_intersection(parking_buffer)

flatparkingstream <- flatparking %>%
  st_intersection(streams_buffer)

fpsr <- flatparkingstream %>%
  st_difference(researchbuffer)

fpsrc <- fpsr %>%
  st_difference(ccbuffer)

campsite1 <- point_to_sf(-72.678393, 42.444742)


leaflet() %>%
  addTiles() %>%
  addPolygons(data = aggforests, 
              color = ~forestpalette(aggforests$Sheet1__Na), 
              fillOpacity = 1) %>%
  addLegend("bottomright", 
            pal = forestpalette,
            values = aggforests$Sheet1__Na,
            opacity = 1) %>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite") %>%
  addMarkers(data = campsite1, popup = "Campsite 1") %>%
  addPolygons(data = fpsrc, color = "red")
```
 
# Campsite 2
 
Same process as in campsite 1.
```{r, warning = FALSE, message = FALSE}
flatparkingwet <- flatparking %>%
  st_intersection(wetlandbuffer)

flatparkingwetr <- flatparkingwet %>%
st_difference(researchbuffer)


flatpwrc <- flatparkingwetr %>%
  st_difference(ccbuffer)

campsite2 <- point_to_sf(-72.675647, 42.446949)

leaflet() %>%
  addTiles() %>%
  addPolygons(data=aggforests,
              color = ~forestpalette(aggforests$Sheet1__Na),
              fillOpacity = 1) %>%
  addLegend("bottomright",
            pal = forestpalette,
            values = aggforests$Sheet1__Na,
            opacity = 1) %>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite") %>%
  addMarkers(data = campsite2, popup = "Campsite 2") %>%
  addPolygons(data = flatpwrc, color = "red")
```

# Final Plot of Proposed Sites
```{r}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = aggforests,
              color = ~forestpalette(aggforests$Sheet1__Na),
              fillOpacity = 1) %>%
  addLegend("bottomright",
            pal = forestpalette,
            values = aggforests$Sheet1__Na,
            opacity = 1)
```

# Problem statement
Macleish has two campsites: one near the Bechtel Environmental Classroom, and one remote campsite about a mile from the parking area. They are looking for a new campsite that has the following conditions: around half a mile from the parking area, precisely 200 feet from a source of water, in a different forest from the forest in the two other campsites, flat, and must be at least 500 feet either from a research area or a Challenge Course.  

# Data
We used Macleish package, and included layers such as trails, boundary, streams, wetlands, forests, research, buildings, landmarks, challenge courses and contours_3m, in order to find the new campsite. In order to see where possible locations  for a campsite were, and what areas of the property were off limits we used a series of buffers around these data. For example, we set up a half mile buffer around the parking lot in order to see what parts of the property were close enough to it to become a campsite. (See inline annotations for wrangling, analysis) 

# Conclusion
According to our leaflet map, the new campsite should be located either in the sugar maple forest or the old white pine forest. The sugar maple forest is a good forest to camp at because it is relatively flat and dry. Initially, we were concerned that camping would affect the maple syrup collection. However, Reid assured us that the tapping season usually takes place during the period where people do not usually camp due to the freezing cold weather at night. Therefore, having a campsite in sugar maple forest would not disrupt the tapping procedure. According to the National Park Service, if the area has many dead trees, it could be hazard to camp because there is a chance that the trees may fall and injure campers.[^2]

One of the major roadblocks on building a new campsite is getting the materials into the forest. Even though the sugar maple forest is relatively close to the parking space or the main build building, it could still cause difficulties in getting the construction materials into the selected forest because the staff members have to carry them from the parking lot or the main building, which could be labour intensive and slow down the process of construction.  We estimated that it would take around a month, depending on the time of year and weather. We estimate the cost to be around $4000 to build a new campsite. This approximation is based on the cost of building the wooden lean-to in the group campsite, which cost $3000 for lumber and transportation. The extra $100 is for other work that may be involved such as clearing the campsite of vegetation, etc. There are also some environmental impacts that should be considered prior to building the new campsite: disposal of waste and hazard of campfire. Campers may not dispose waste properly and leave their waste behind, such as food scraps. Moreover, campfire may generate light and smoke pollution to the forest. These actions may cause disturbance to the environment and animals that live in the forest.[^3]



[^1]: https://github.com/ireneryan/sds192-mp3
[^2]: https://www.nps.gov/subjects/camping/finding-and-setting-up-a-campsite.htm
[^3]: https://www.campjellystone.com/leave-no-trace-7-principles-reduce-environment-impact/