---
title: "mp3"
output: html_document
---
QUESTIONS FOR WEDNESDAY:

Make sure buffers are right size
Remote Campsite location???
Forest Aggregation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(macleish)
library(tidyverse)
library(sf)
library(leaflet)
library(data.table)
library(units)
```

```{r}
trails<-macleish_layers[["trails"]]
boundary<-macleish_layers[["boundary"]]

streams<-macleish_layers[["streams"]]
wetlands<-macleish_layers[["wetlands"]]

forests<-macleish_layers[["forests"]]

research<-macleish_layers[["research"]]
buildings<-macleish_layers[["buildings"]]

landmarks<-macleish_layers[["landmarks"]]
challengecourses<-macleish_layers[["challenge_courses"]]

contours <- macleish_layers[["contours_3m"]]

```

```{r}
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=42.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

point_to_sf <- function(lat, lon) {
  st_point(c(lat,lon)) %>%
    st_sfc(crs = 4326)
}

parking <- point_to_sf(-72.680663, 42.448013) %>%
  st_transform(crs = proj4_aea)
group_campsite <- point_to_sf(-72.678154, 42.450976)
remote_campsite <- point_to_sf(-72.674732, 42.458570)

# put 1/2 mi (804.672 m) buffer around parking area
parking_buffer <- st_buffer(parking, dist = 402.336) %>%
  st_transform(crs = 4326)

streams_inside <- boundary %>%
  st_intersection(streams)

library(units)

parkbuffer<-parking%>%
  st_transform(proj4_aea)%>%
  st_buffer(dist= 402.336)%>%
  st_transform(4326)
  
streams_buffer <- streams_inside %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 30.48) %>%
  st_transform(4326)

ccbuffer<-challengecourses%>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)

researchbuffer<-research%>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)

wetlandbuffer<-wetlands%>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 68.58) %>%
  st_transform(4326)
```


MacLeish currently has two campsites - one large group site closer to the building and one remote campsite with two tent platforms about one mile from the parking area. We would like to develop one additional campsite that is approximately half a mile walk from the parking area, within 200’ of a stream or other source of water, in forest that is unlike the forest in the two other campsites, relatively flat, and at least 500’ from any research area or any element of the Challenge Course. Propose two new campsite locations for our consideration.
Supporting data includes:
Existing trails shapefile
10’ contour elevation data
vegetation type shapefile
hydrology (streams, wetlands, etc.) shapefile
Research locations shapefile
Challenge course element locations shapefile
Property Boundary shapefile
=======
```{r}

library(macleish)

bechtel <- data.frame(lat = 42.449167, lon = -72.679389)

aggforests<-forests%>%
  group_by(Sheet1__Na)%>%
  summarise(n=n())

forestpalette<-colorFactor(palette = "viridis",
                    domain = aggforests$Sheet1__Na)

library(RColorBrewer)

pale <- colorNumeric(palette = "inferno",
                    domain = contours$ELEV_M)

leaflet() %>%
  addTiles %>%
  addPolygons(data = boundary, weight = 1, fillOpacity = 0.1) %>%
  addMarkers(data = st_transform(parking, crs = 4326), popup = "Parking") %>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite") %>%
addPolygons(data = parking_buffer, color = "green") %>%
  addPolygons(data = buildings, weight = 1, opacity = 1)%>%
  addPolylines(data = streams_buffer, fillOpacity = 0.5, color="green")%>%
  addPolygons(data = researchbuffer,fillOpacity = 0, weight=.5)%>%
  addPolygons(data=ccbuffer, fillOpacity = 0, weight=.5)%>%
  addPolygons(data=wetlands)%>%
  addMarkers(data=challengecourses)%>%
  addPolygons(data=research)%>%
  addMarkers(lng = ~lon, lat = ~lat, data = bechtel,
             popup = "Bechtel Environmental Classroom") %>%
  addPolygons(data = contours, color = ~pale(ELEV_M), weight = 0.5) %>%
  addPolygons(data=wetlandbuffer, color="green")
  addLegend("bottomright", pal = pale, values = contours$ELEV_M)
```

#Campsite 1

```{r}
flatland<-contours%>%
  filter(ELEV_M<=220)

flatparking<-flatland%>%
  st_intersection(parking_buffer)

flatparkingstream<-flatparking%>%
  st_intersection(streams_buffer)

fpsr<-flatparkingstream%>%
  st_difference(researchbuffer)

fpsrc<-fpsr%>%
  st_difference(ccbuffer)

leaflet()%>%
  addTiles%>%
  addPolygons(data=aggforests, color = ~forestpalette(aggforests$Sheet1__Na), fillOpacity = 1)%>%
  addLegend("bottomright", pal = forestpalette, values = aggforests$Sheet1__Na)%>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite")%>%
    addPolygons(data=fpsrc)
```
 
```{r}
flatparkingwet<-flatparking%>%
  st_intersection(wetlandbuffer)

flatparkingwetr<-flatparkingwet%>%
st_difference(researchbuffer)

flatpwrc<-flatparkingwetr%>%
  st_difference(ccbuffer)

leaflet()%>%
  addTiles%>%
  addPolygons(data=aggforests, color = ~forestpalette(aggforests$Sheet1__Na), fillOpacity = 1)%>%
  addLegend("bottomright", pal = forestpalette, values = aggforests$Sheet1__Na)%>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite")%>%
    addPolygons(data=flatpwrc)
```


MacLeish currently has two campsites - one large group site closer to the building and one remote campsite with two tent platforms about one mile from the parking area. 
We would like to develop one additional campsite that is approximately half a mile walk from the parking area, 
within 200’ of a stream or other source of water, 
in forest that is unlike the forest in the two other campsites, 
relatively flat, and at
least 500’ from any research area or any element of the Challenge Course. 

Propose two new campsite locations for our consideration.



Group Campsite (42.450976, -72.678154)
Remote Campite (42.458570, -72.674732)
Parking (42.448013, -72.680663)



