---
title: "mp3"
output: html_document
---

Group Campsite (42.450976, -72.678154)
Remote Campite (42.458570, -72.674732)
Parking (42.448013, -72.680663)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(macleish)
library(sf)
```

```{r}
trails<-macleish_layers[["trails"]]
boundary<-macleish_layers[["boundary"]]

streams<-macleish_layers[["streams"]]
wetlands<-macleish_layers[["wetlands"]]

forests<-macleish_layers[["forests"]]

research<-macleish_layers[["research"]]
buildings<-macleish_layers[["buildings"]]

landmarks<-macleish_layers[["landmarks"]]
challengecourses<-macleish_layers[["challenge_courses"]]
```

```{r, eval=FALSE}
url <- "http://wsgw.mass.gov/data/gispub/shape/state/contours250k.zip"
local_file <- basename(url)
download.file(url, destfile = local_file)
unzip(local_file, exdir = "contour")
```

```{r}
library(sf)
dsn <- path.expand("contour")
dsn
list.files(dsn)
contour_layer <- read_sf(dsn)
st_layers(dsn)

contour_layer <- st_transform(contour_layer, crs = 4326)

boundelev<-macleish_layers[["boundary"]]%>%
  st_intersection(contour_layer)

boundelev%>%
  plot()
 
boundelev %>%
  arrange(CONTOUR_FT)

proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=42.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

point_to_sf <- function(lat, lon) {
  st_point(c(lat,lon)) %>%
    st_sfc(crs = 4326)
}

parking <- point_to_sf(-72.680663, 42.448013) %>%
  st_transform(crs = proj4_aea)
group_campsite <- point_to_sf(-72.678154, 42.450976)
remote_campsite <- point_to_sf(-72.674732, 42.458570)

 
 

library(leaflet)
leaflet() %>%
  addTiles %>%
  addPolygons(data = boundary, weight = 1, fillOpacity = 0.1) %>%
  addMarkers(data = st_transform(parking, crs = 4326), popup = "Parking") %>%
  addMarkers(data = group_campsite, popup = "Group Campsite") %>%
  addMarkers(data = remote_campsite, popup = "Remote Campsite") %>%
  addPolygons(data = parking_buffer, weight = 1, opacity = 0.1) %>%
  addPolygons(data = buildings, weight = 1, opacity = 1) 
#1/2 mile from parking area

#within 200` of a stream/water source

#in a forest unlike the forest the other 2 are in

#relatively flat

#at least 500` from any research area or challenge course

library(data.table)
campground<-data.table(campsite=c("Group Campsite", "Remote Campsite"), longitude=c(42.450976, 42.458570), latitude=c(-72.678154, -72.674732))

campgroundsf<-st_as_sf(campground, coords = c("longitude", "latitude"), crs = 4326)

parking<-data.table(parking="Parking lot", longitude=42.448013, latitude=-72.680663)

parkingsf<-st_as_sf(parking, coords = c("longitude", "latitude"), crs = 4326)

```


MacLeish currently has two campsites - one large group site closer to the building and one remote campsite with two tent platforms about one mile from the parking area. We would like to develop one additional campsite that is approximately half a mile walk from the parking area, within 200’ of a stream or other source of water, in forest that is unlike the forest in the two other campsites, relatively flat, and at least 500’ from any research area or any element of the Challenge Course. Propose two new campsite locations for our consideration.
Supporting data includes:
Existing trails shapefile
10’ contour elevation data
vegetation type shapefile
hydrology (streams, wetlands, etc.) shapefile
Research locations shapefile
Challenge course element locations shapefile
Property Boundary shapefile


1/2 mile from parking area
within 200` of a stream/water source
in a forest unlike the forest the other 2 are in
relatively flat
at least 500` from any research area or challenge course
```{r}

```

